How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-06-14 paper.tex
some new text

In all of these cases, it is necessary to interact with the people who develop
and support the code. How you go about it has an enormous impact on your
likelihood of success and how you are viewed, but this is not something that is
explicitly taught in most places.  {\emph The goal of this paper is to reveal
the hidden curriculum -- what's expected of a software consumer, how to ask for
help, how to contribute productively to a software community (regardless of
whether you can write code).}

Asking strangers for help can be intimidating, regardless of your

There lots of articles on best practices in software development, including open
source.

emphasize the idea of a social contract: what do developers owe the users, what
do users owe developers, what do users owe other users

@@

>>>>

In all of these cases, it is necessary to interact with the people who develop
and support the code. How you go about it has an enormous impact on your
likelihood of success and how you are viewed, and asking complete strangers for
help is often intimidating, especially the first time you do it. However, the
best way to do so is rarely taught explicitly --- at best, it's something one
picks up by example, from fellow lab members or the PI.  {\emph The goal of this
paper is to reveal the hidden curriculum -- what's expected of a software
consumer, how to ask for help, how to contribute productively to a software
community (regardless of whether you can write code).}

This article is written from a perspective of academic open-source scientific
software. Much of what we suggest is universal, but some points --- like the
reminder that the people providing the support are likely volunteers --- are
not.  Regardless, we view the interaction between developers and users as an
informal social contract, where each has obligations and expectations for the
other. Obviously, every software community is unique, and many have specific
conventions for interaction, but we hope that the recommendations we make are at
the very least a good starting point for new users of scientific software.

@@

\section{Good practices in asking for help}

\section{Obligations of software developers}

This paper has focused on what software consumers should do when asking for
help.  However, this does not mean that the developers of scientific software
are without responsibilities. If we want users to behave in a certain way, it
behooves us to tell them that. Users approaching us in good faith deserve to be
treated fairly and courteously.
